30June16 explant sups plate 3: MIG, RANTES, IL1ra

### 2016-07-15 30June16_plate_3_explant_sup.Rmd
formatted the individual plots differently, added a plot with all analytes

@@

Here is a plot of the % recovery (extrapolated concentration/ known concentration x 100) for the standards that were in the detection range, with lines at the "good recovery" limits of 80 and 120% recovery.

@@

stdFit<- standardsInRange %>% 
  arrange(Sample,Assay)%>%
  select(Type, Sample, Assay, X..Recovery,Fit.Statistic..RSquared, Concentration, Calc..Concentration)

ggplot(stdFit, aes(x = Sample, y = X..Recovery))+
  geom_point(aes(color = Sample))+
  facet_wrap(~Assay)+
  theme(axis.text.x = element_text(angle=25))+
  scale_y_continuous(limits = c(75, 200))+
  geom_abline(slope = 0, intercept = c(80, 120))+
  labs(y = "Percent Recovery")+
  theme(axis.text.x = element_text(size = rel(0.8)))

@@

@@

# AvgConcExplantDat <- explantDat %>%
#   group_by(Sample, Assay, Donor, Timepoint,Virus, Detection.Range)%>%
#   summarize(avgConc = mean(Calc..Concentration))
```

@@

  geom_point(aes(color = Donor, shape = Detection.Range ),size = 1, alpha = 0.5 )+

@@

  facet_wrap(~Timepoint)+

Another way of looking at the data

```{r MIG alternate, echo=FALSE, warning=FALSE, message= FALSE}

ggplot(data = MIGexplantDat, aes(x = Timepoint, y = Calc..Concentration))+

  geom_point(aes(color = Donor, shape = Detection.Range ),size = 1, alpha = 0.5 )+

  #stat_summary(aes(group = Donor, color = Donor), fun.y =mean, geom = "line")+

  scale_shape_manual(values = c("Above Fit Curve Range" = 1, "In Detection Range" = 16))+

  facet_wrap(~Virus)+

@@

  facet_wrap(~Timepoint)+

@@

```{r RANTES alternate, echo=FALSE, warning=FALSE, message= FALSE}

ggplot(data = RANTESexplantDat, aes(x = Timepoint, y = Calc..Concentration))+

  geom_point(aes(color = Donor, shape = Detection.Range ),size = 1, alpha = 0.5 )+

  #stat_summary(aes(group = Donor, color = Donor), fun.y =mean, geom = "line")+

  facet_wrap(~Virus)+
  ggtitle("RANTES data")

@@

```{r IL1RA alternate, echo=FALSE, warning=FALSE, message= FALSE}

ggplot(data = IL1RAexplantDat, aes(x = Timepoint, y = Calc..Concentration))+

  geom_point(aes(color = Donor, shape = Detection.Range ),size = 1, alpha = 0.5 )+

  #stat_summary(aes(group = Donor, color = Donor), fun.y =mean, geom = "line")+

  facet_wrap(~Virus)+
  ggtitle("IL1RA data")
```

>>>>

### Formatting note: In the data table, there is both " T3" and "T3" so I am fixing it here.

dat$Sample<- str_replace(dat$Sample, " T3", "T3")

@@

Here is a plot of the % recovery (extrapolated concentration/ known concentration x 100) for the standards that were either within or above the detection range, with lines at the "good recovery" limits of 80 and 120% recovery.

@@

stdFit<- standards %>% 
  arrange(Sample,Assay)%>%
  filter(Detection.Range != "Below Fit Curve Range")%>%
  select(Type, Sample, Assay,Detection.Range, X..Recovery,Fit.Statistic..RSquared, Concentration, Calc..Concentration)

ggplot(stdFit, aes(x = Sample, y = X..Recovery))+
  geom_point(aes(color = Sample, shape = Detection.Range ),size = 3)+
  scale_shape_manual(values = c("Above Fit Curve Range" = 1, "In Detection Range" = 16))+
  facet_wrap(~Assay)+
  theme(axis.text.x = element_text(angle=25))+
  scale_y_continuous(limits = c(75, 200))+
  geom_abline(slope = 0, intercept = c(80, 120))+
  labs(y = "Percent Recovery")+
  theme(axis.text.x = element_text(size = rel(0.8)))

@@

```{r standard curves, echo=FALSE, warning=FALSE, message= FALSE}

# standardCurve<- function (Calc.Top, Calc.Bottom, Calc.HillSlope, Calc.Midpoint, Concentration){
# 
# Calc.Top + (Calc.Bottom - Calc.Top/(1+(Concentration/Calc.Midpoint)^Calc.HillSlope))
# }
# 
# 
# MIGcurveData <- standards%>%
#   filter(Assay == "MIG") %>%
#   mutate(UpperLimit = Algorithm.Parameter..Calc..Top-( Detection.Limits..Top.of.Range.Parameter * Std..Deviation ))%>%
#   mutate(LowerLimit = min(Concentration)+(2.5 * Std..Deviation ))
# 
# 
# 
# MIGcalcCurve <- standardCurve(MIGcurveData$Algorithm.Parameter..Calc..Top,MIGcurveData$Algorithm.Parameter..Calc..Bottom, MIGcurveData$Algorithm.Parameter..Calc..HillSlope, MIGcurveData$Algorithm.Parameter..Calc..MidPoint, MIGcurveData$Concentration)
# 
# 
# ggplot(MIGcurveData, aes(x = Concentration, y = Signal))+
#   geom_point()+
#   scale_y_log10()+
#   scale_x_log10()+
#   geom_line(aes(y = MIGcalcCurve))+
#   geom_hline(yintercept = MIGcurveData$UpperLimit)

@@

# AvgConcExplantDat <- explantDat %>%
#   group_by(Sample, Assay, Donor, Timepoint,Virus, Detection.Range)%>%
#   summarize(avgConc = mean(Calc..Concentration))
```
## Caveats

Some data points were above the range of the curve fit. The MSD software can extrapolate values for these if the curve is linear at the top. Values cannot be extrapolated when the data was below the fit curve range, so those are not shown in the following plots.

```{r everything, echo=FALSE, warning=FALSE, message= FALSE}

ggplot(explantDat, aes(x = Virus, y = Calc..Concentration))+

  geom_point(aes(color = Assay, shape = Detection.Range ),size = 1.5)+

  facet_wrap(Timepoint~Donor, scales = "free_x")+

  theme(axis.text.x = element_text(angle = 25, size = 9))+

  ggtitle("Data from all analytes")

@@

  geom_point(aes(color = Donor, shape = Detection.Range ),size = 1, alpha = 0.5, position = position_swarm(0.5) )+

@@

  facet_wrap(Timepoint ~ Donor, scales = "free_x")+

@@

  facet_wrap(Timepoint ~ Donor, scales = "free_x")+

@@

@@
